\documentclass[letter]{report}
\usepackage{charter}
\usepackage{hyperref}
\pagestyle{empty}

\begin{document}

\title{Basic Rules for the Governance of the Linux User Group at the University of Illinois at Chicago}
\author{Linux User Group @ UIC\\
	University of Illinois at Chicago\\
		Chicago, IL\\
		United States\\
		\url{lug.cs.uic.edu}}
\date{\today}
\maketitle


\begin{abstract}
\noindent This document defines the operative principles for the Linux Users Group at the University of Illinois at Chicago.
\end{abstract}

\part{NAME AND OBJECTIVE}
\section{Name of Organization}
\subsection{This organization shall be known as the Linux Users Group or ``LUG" for short.  It shall henceforth be referred to as LUG within this document}  

\section{Objective}
\subsection{The objective of this organization shall be to promote the use, understanding, and awareness of the Linux operating system; in addition to open source software and related technologies.}

\part{MEMBERSHIP}
\section{Eligibility}
\subsection{Membership shall be limited to students, faculty, staff, and alumni of the University of Illinois at Chicago (UIC); as well as members not affiliated with the university.}
\subsection{Membership shall not in any way be contingent upon prior knowledge, experience, or field of study.}
\subsection{Membership and participation shall be free from discrimination based upon gender, race, religion, physical disability, or sexual orientation.}
\section{Status}
\subsection{Membership shall be divided into three groups: Active and Members-At-Large.}
\subsection{Active members are those individuals who are considered to be in good standing within the organization. Initial Active status shall be granted to any Member-At-Large attending a scheduled organization gathering. Active member status is restricted to those directly affiliated with the University.
}
\subsection{Members-at-Large are considered to be any and all members who are not of Active status. Initial Member-at-Large status shall be granted to any eligible individual upon written request.
}
\subsection{All written requests for membership status shall be considered by the Executive Committee.}
\subsection{The Executive Committee shall periodically review membership activity and make appropriate status adjustments.}
\section{Registration}
\subsection{To register a member must find a Linux Users Group officer and and request a membership form. Upon completion of this form this person shall be considered a member of the Linux Users Group. In order to remain a member in active status one must repeat this process annually.}

\section{Standing}
\subsection{Active members must meet the following requirements in order to be considered in ``good standing" by the organization:}
\begin{itemize}
\item {Members shall contribute to meetings and activities.}
\item {Members shall uphold and complete all duties and responsibilities assigned them as officers and members.}
\end{itemize}
\subsection{Any member who does not meet the above requirements for good standing shall be assigned Member-At-Large status at the discretion of the Executive Committee.}

\section{Expulsion}
\subsection{A member may be expelled from the LUG for any or all of the following reasons:}
\begin{itemize}
	\item Stealing or the abuse of funds.
	\item Physical or verbal abuse of other members.
	\item Any gross misconduct as so deemed by the Executive Committee.
\end{itemize}
\subsection{ In order for a member to be expelled, a majority vote (50\%)+1 must be obtained from all voting members.  A week long voting session will be held where all eligible voting members may cast their votes.  At the end of the voting period, the votes will be tallied and the necessary action will be taken.}  

\subsection{The elected officers reserve the right to declare an emergency expulsion where the officers feel that the accused's misconduct calls for such an action.  This action requires a full approval of all the elected officers requiring a unanimous vote for the motion to pass }

\part{OFFICERS}
\section{Executive Officers}
\subsection{Executive officers shall include the President, Vice President, and Treasurer.}
\subsection{Executive officers shall be chosen by the organization through the process of elections.}
\section{Non-Executive Officers}
\subsection{Non-Executive officers may include, but are not limited to, the Secretary, the Webmaster and a Funding Officer.}
\subsection{Non-Executive officers shall be appointed by the Executive Committee, who shall make its decision from among all eligible applicants.}
\section{Elective Eligibility}
\subsection{Only Active members in good standing shall be eligible for election to office within the LUG.}
\subsection{Neither faculty, staff, nor alumni may serve as executive officers.}
\section{Terms of Office}
\subsection{The term of office for all officers shall be one calendar year.}
\subsection{There shall be no enforced term limit.}
\section{Election Procedures}
\subsection{The election of officers shall be held annually.}
\subsection{Only Active members are eligible to vote and must be present in person at the time of the election in order to cast their vote.}
\subsection{A quorum of five Active members must be present in order to conduct an election.}
\subsection{A candidate must achieve a 50\%+1 majority to win an election.}
\subsection{If a majority vote is not obtained, a runoff election between the two top-scoring candidates may be held for purposes of deciding the victor.}
\section{Officers' Duties}
\subsection{President}
\begin{itemize}
\item The president shall have the power to establish new projects and enter into new business transactions on behalf of and given the approval of, the Executive Committee.
\item The President shall have the power to establish new offices and to fill vacancies in existing offices should such vacancies occur.
\item The President shall preside at all scheduled organization gatherings.
\item The President shall assume all other executive duties not otherwise explicitly delegated.
\end{itemize}
\subsection{Vice-President}
\begin{itemize}
\item The Vice-President shall assume all functions of the President should the latter be absent or unable to perform his duties.
\item The Vice-President shall serve as the project leader on and shall have sole authority over the LUG's primary design project and--as such--shall be responsible for the management, budgeting, and timely delivery of said Project.
\end{itemize}
\subsection{Treasurer}
\begin{itemize}
\item The Treasurer shall receive all funds payable and reconcile all debts of the LUG as so authorized by the Executive Committee.
\item The Treasurer shall keep an exact record of all receipts, payouts, and expenditures of the LUG, and shall furthermore make the record available to the Executive Committee at any and all scheduled meetings.
\item The Treasurer shall complete a year-end Financial Statement for inclusion in the Annual Report of Activities.
\end{itemize}
\subsection{Secretary}
\begin{itemize}
\item The Secretary shall create a record of all scheduled activities within the LUG and shall make that record available as minutes to all active members within one week of the activity via electronic means.
\item The Secretary shall be responsible for preparing all administrative paperwork necessary to expediting the operation of the LUG.
\item The Secretary shall coordinate the operation of the listserv and the website with the Webmaster.
\item The Secretary shall be responsible for the creation of all promotional and/or informational posters and fliers for the LUG.
\item The Secretary shall provide all records of the previous year in the Annual Report of Activities.
\end{itemize}
\subsection{Webmaster}
\begin{itemize}
\item The Webmaster shall be responsible for the content and design of both the public and private websites for the LUG.
\item The Webmaster shall maintain any listserv related tasks.
\end{itemize}

\section{Impeachment}
\subsection{Any officer found to be grossly incompetent, irresponsible, or negligent of his or her duties may be recommended for impeachment.}
\subsection{For a recommendation of impeachment to be approved, a three-quarters majority of all Active members is necessary.}
\subsection{Any individual successfully impeached from office shall be notified no later than forty-eight hours from the completion of the vote for impeachment.}

\part{EXECUTIVE COMMITTEE}
\section{Structure}
\subsection{The Executive Committee shall be comprised of the President, Vice-President, and Treasurer.}
\section{Duties}
\subsection{The Executive Committee shall be the primary governing body of the LUG.}
\subsection{The Executive Committee shall conduct--on behalf of the LUG--all business it deems necessary, including--but not limited to--the filling of vacancies and/or the creation of offices and the authorization of expenditures.
}
\subsection{The Executive Committee shall eliminate any unnecessary office(s) not provided for in The Constitution.}
\section{Approval}
\subsection{When the approval of the Executive Committee is required of any action, a three-quarters majority of the Committee shall suffice for purposes of approval; unless otherwise dictated.}
\part{MEETINGS}
\section{General Meetings}
\subsection{General Meetings shall be held a minimum of once per academic year.}

\section{Regular Meetings}
\subsection{Regular meetings shall be held on a weekly basis and shall consist of:}\
\begin{itemize}
\item A brief discussion of current affairs moderated by the Executive Committee.
\item A presentation or lead discussion from a preselected member; following which, the presenter shall assign another member to present during the next week's meeting.
\end{itemize}
\subsection{Meeting time and location shall be decided by the Executive Committee at the beginning of each semester. The decision will be based on a survey of the Active members.}
\subsection{Cancellation or suspension of weekly meetings may be requested at any time from an Active member, and shall be contingent upon the approval of the Executive Committee.}
\section{Special Meetings}
\subsection{Special Meetings may be requested at any time by an Active member, and shall be contingent upon the approval of the Executive Committee.}

\part{DUES}
\section{Dues}
\subsection{The LUG shall not hold the power to levy dues.  Donations may be recommended for certain goods and services which have to be approved by the Executive Committee.}   
\section{Special Assessments}
\subsection{The Executive Committee shall have the power to levy a one-time assessment on members for unique and irregular activities and services.}

\part{ADVISER}
\section{The LUG shall enlist the assistance of an adviser on all projects. The LUG adviser shall be a full-time faculty member at UIC.}

\part{AMENDMENTS AND REVISIONS}
\section{Proposition}
\subsection{Active members may, whenever they deem necessary, propose amendments or revisions to the LUG Constitution.}
\section{Dissemination}
\subsection{Any proposed amendment or revision shall be formally submitted to the Executive Committee and subsequently disseminated to all active members of the LUG at a minimum of one week prior to the calling of a vote.}
\section{Requirements}
\subsection{Any vote for an amendment or revision to the LUG Constitution requires a quorum of seven Active members.}
\section{Ratification}
\subsection{For an amendment to be successfully ratified, a three-quarters majority of all present and voting members must be obtained.}

\part{RATIFICATION}
\section{The full agreement of the standing Executive Officers and one additional Active member shall be sufficient for the establishment of this Constitution of the Linux Users Group at the University of Illinois at Chicago. Done through authorized consent of the undersigned members present this seventh day of December in the year two-thousand five.
}
(signed)
\end{document}  %End of document.
